Hector Permafrost

### 2020-03-17 analysis/paper/paper.Rmd
Remove deprecated functions from paper

```{r setup, echo = FALSE}
library(drake)
library(knitr)
library(here)
library(dplyr)
library(ggplot2)

@@

# Dummy target to force-rebuild this when figures change
invisible(readd(figs_dir_t))

fig <- function(...) {
  filepath <- here("analysis", "figures", ...)
  knitr::include_graphics(file_in(filepath))
}

n <- 0
mdcap <- function(text) {
  n <<- n + 1
  out <- sprintf("**Figure %d**: %s", n, text)
  if (grepl("gfm", knitr::opts_knit$get("rmarkdown.pandoc.to"), ignore.case = TRUE)) {
    out
  } else {
    invisible(NULL)
  }
}

m <- 0
htmlfig <- function() {
  m <<- m + 1
  out <- paste0("**Figure ", m, "**:")
  if (grepl("html", knitr::opts_knit$get("rmarkdown.pandoc.to"), ignore.case = TRUE)) {
    out
  } else {
    invisible(NULL)
  }
}
```

>>>>

```{r setup, echo = FALSE}
library(knitr)
library(here)
library(dplyr)
library(ggplot2)

@@

fig <- function(...) {
  filepath <- here("analysis", "figures", ...)
  knitr::include_graphics(file_in(filepath))
}
```
